Chapter3_ideas

### 2019-12-08 results/Chapter3_ideas.Rmd
fixed version of position randomization loop

pos.pool_1CO <- male.whole.cell[male.whole.cell$hand.foci.count == 1,]
pos.pool_2CO <- male.whole.cell[male.whole.cell$hand.foci.count == 2,]
pos.pool_3CO <- male.whole.cell[male.whole.cell$hand.foci.count == 3,]

#now make the randomized data set for CO pos
#do whole row -- so I can cen n

>>>>

male.whole.cell <- male.whole.cell[!(is.na(male.whole.cell$fileName) | male.whole.cell$fileName==""), ]

#make sure male.whole.cell has nrm oci positions
pos.pool_1CO <- male.whole.cell[male.whole.cell$hand.foci.count == 1,]
pos.pool_2CO <- male.whole.cell[male.whole.cell$hand.foci.count == 2,]
pos.pool_3CO <- male.whole.cell[male.whole.cell$hand.foci.count == 3,]

pos.pool_1CO <- pos.pool_1CO[!(is.na(pos.pool_1CO$fileName) | pos.pool_1CO$fileName==""), ]
pos.pool_2CO <- pos.pool_2CO[!(is.na(pos.pool_2CO$fileName) | pos.pool_2CO$fileName==""), ]
pos.pool_3CO <- pos.pool_3CO[!(is.na(pos.pool_3CO$fileName) | pos.pool_3CO$fileName==""), ]
#now make the randomized data set for CO pos
#do whole row -- so I can cen n

male.whole.cell.mini <- male.whole.cell#[190:455, ]

for(oar in 1:length(male.whole.cell.mini$fileName)){
  print(oar)
   if(male.whole.cell.mini$hand.foci.count[oar] == 1){
    print("oner")
     #random sample
     rand.obj.id.1CO <- sample(pos.pool_1CO$Obj.ID, 1)

     male.whole.cell.mini$rand.ID[oar] <- rand.obj.id.1CO
     male.whole.cell.mini$rand.Foci1[oar] <- as.numeric(pos.pool_1CO$Foci1[which(pos.pool_1CO$Obj.ID == rand.obj.id.1CO)])
     #  sample(pos.pool_1CO$F1, 1, replace = FALSE)
     male.whole.cell.mini$rand.Foci2[oar] <- ""
     male.whole.cell.mini$rand.Foci3[oar] <- ""
   }

  if(male.whole.cell.mini$hand.foci.count[oar] == 2){
    print("twoer")

    #random sampl of obj.id
    rand.obj.id <- sample(pos.pool_2CO$Obj.ID, 1)

    male.whole.cell.mini$rand.ID[oar] <- rand.obj.id
    #asign the F1s and F2s from the fit obj.id

    male.whole.cell.mini$rand.Foci1[oar] <-as.numeric(pos.pool_2CO$Foci1[which(pos.pool_2CO$Obj.ID == rand.obj.id)])
  #  male.whole.cell.mini$rand.Foci2[oar] <- "blah"
    male.whole.cell.mini$rand.Foci2[oar] <-as.numeric(pos.pool_2CO$Foci2[which(pos.pool_2CO$Obj.ID == rand.obj.id)])
    male.whole.cell.mini$rand.Foci3[oar] <- ""
 }

  if(male.whole.cell.mini$hand.foci.count[oar] == 3){
    print("threer")
    rand.obj.id_3co <- sample(pos.pool_3CO$Obj.ID, 1)

    male.whole.cell.mini$rand.ID[oar] <- rand.obj.id_3co

        male.whole.cell.mini$rand.Foci1[oar] <-as.numeric(pos.pool_3CO$Foci1[which(pos.pool_3CO$Obj.ID == rand.obj.id_3co)])
  #  male.whole.cell.mini$rand.Foci2[oar] <- "blah"
    male.whole.cell.mini$rand.Foci2[oar] <-as.numeric(pos.pool_3CO$Foci2[which(pos.pool_3CO$Obj.ID == rand.obj.id_3co)])

    male.whole.cell.mini$rand.Foci3[oar] <-as.numeric(pos.pool_3CO$Foci2[which(pos.pool_3CO$Obj.ID == rand.obj.id_3co)])
